Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method

### 2019-10-24 rainbowCAM.tex
few typos corrected
Checking some resulats
some minor rewording

\usepackage{graphicx, epsfig, amssymb}
\usepackage{amsmath, amsfonts}
\usepackage{bm}
\usepackage{enumitem}
\usepackage[usenames]{color}
\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
\usepackage[linktocpage,colorlinks=true,allcolors=navyblue]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{soul}
%\usepackage{enumerate}
\usepackage{pict2e}
\usepackage{diagbox}
\usepackage{empheq}

@@

\section{Introduction}
Blah. hello. some more text.

@@

In this section, we describe our compact objets model and we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body and we apply the CAM-approach developed in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}

@@

  We consider that the gravitating source a spherically symmetric incompressible perfect fluid ball of uniform
density (see Ref~\cite{Dolan:2017rtj} and reference therein) in a coordinate system $\{t,r,\theta,\varphi\}$ and is defined by the metric
\begin{equation}\label{Line_elem}
  ds^2= -f(r) dt^2+h(r)^{-1}dr^2+r^2d\sigma_2^2
\end{equation}
where $d\sigma_2^2$ denotes the metric on the unit 2-sphere $S^2$. Here, the radial function $h(r)$ is continuous but not differentiable across the surface of the star $r=R$ and the function $f(r)$ is one, but not twice, differentiable. We recall that, in the exterior of the star (i.e., $r>R$), we have $f(r)=h(r)=a-2M/r$ by Birkhoff's~\cite{VojeJohansen:2005nd}. In the interior of the star (i.e. $r<R$), we have the Schwarzschild solution for an incompressible fluid~\cite{Shapiro1983}

\begin{subequations}\label{Interior_Solution}
\begin{align}\label{Interior_Solution_f}
    f(r) =\frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nonumber\\ -\frac{3}{2}
                \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)}
\end{align}
\begin{equation}\label{Interior_Solution_h}
 h(r) =1-\frac{2 M r^2}{R^3}
\end{equation}
\end{subequations}

@@

We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
\begin{equation}\label{Scalar_Scattering_diff}
  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
\end{equation}
where
\begin{equation}\label{Scalar_Scattering_amp}
 \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
\end{equation}
denotes the scattering amplitude.  In Eqs.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.  We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eqs.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ solutions of the homogenous radial equation
\begin{equation}
\label{H_Radial_equation}
\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0
\end{equation}
here $dr/dr^\ast =\sqrt{f(r)h(r)}$ denotes the tortoise coordinate, where
\begin{equation}\label{Inside_Potentiel}
  V_{\ell}(r) =f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right]
\end{equation}
the potential inside the star ($r<R$) and  $V_{\ell}(r)$ reduces to the Regge-Wheeler potential outside the star ($r>R$)
\begin{equation}\label{RW_Potentiel}
  V_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M}{r^3}\right)
\end{equation}
and the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+\mathrm{const}$.

It is important to recall that the modes $\phi_{\omega \ell}$ have a regular behavior at the origin $r \to 0$
\begin{equation}\label{bc_1_in}
\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}
\displaystyle{r^{\ell+1}}.
\end{equation}
of the compact body and an asymptotic behavior at spatial infinity $r \to +\infty$ (i.e., for $r_\ast \to +\infty$) of the form
\begin{equation}\label{bc_2_in}
\phi_{\omega  \ell}(r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
\displaystyle{ A^{(-)}_\ell (\omega) e^{-i\omega r_\ast} + A^{(+)}_\ell (\omega) e^{+i\omega r_\ast}}.
\end{equation}
In this last equation, the coefficients $A^{(-)}_\ell (\omega)$ and  $A^{(+)}_\ell (\omega)$ are complex amplitudes and we have
\begin{equation}\label{Matrix_S}
  S_{\ell}(\omega) =  e^{i(\ell+1)\pi} \, \frac{A_{\ell}^{(+)}(\omega)}{A_{\ell}^{(-)}(\omega)}.
\end{equation}

@@

By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
\begin{equation}\label{SWT_gen}
\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
\end{equation}
with a function $F$ without any singularities on the real $\lambda$ axis,we replace in Eq.~(\ref{Scalar_Scattering_amp}) the discrete sum over the ordinary angular momentum $\ell$ by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$). By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
\end{eqnarray}
In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).

Here, we note that, the Legendre function of first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$. It is defined in terms of hypergeometric functions by \cite{AS65}
\begin{equation}\label{Def_ext_LegendreP}
P_{\lambda -1/2} (z) = F[1/2-\lambda,1/2+\lambda;1;(1-z)/2].
\end{equation}
In Eq.~(\ref{SW_Scalar_Scattering_amp}), $S_{\lambda -1/2} (\omega)$ denotes ``the'' analytic extension of $S_\ell (\omega)$. It is given by [see Eq.~(\ref{Matrix_S})]
\begin{equation}\label{Matrix_S_CAM}
  S_{\lambda -1/2}(\omega) =  e^{i(\lambda + 1/2)\pi} \, \frac{A_{\lambda -1/2}^{(+)}(\omega)}{A_{\lambda -1/2}^{(-)}(\omega)}
\end{equation}
where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}$.

It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{PR_def_Am}
A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
\end{equation}
and the associated residues will play a central role. We note that the residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{residues_RP}
r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
\end{equation}

Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using the Cauchy's theorem, the Regge poles contributions. This achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec. IIB~3 and Fig.~1). We obtain

\begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
\hat{f} (\omega, \theta) =  \hat{f}^\text{\tiny{B}} (\omega, \theta) +  \hat{f}^\text{\tiny{RP}} (\omega, \theta)
\end{equation}
where
\begin{subequations}\label{CAM_Scalar_Scattering_amp_decomp}
\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background}
\hat{f}^\text{\tiny{B}} (\omega, \theta) = \hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta)+ \hat{f}^\text{\tiny{B},\tiny{Im}} (\omega, \theta)
\end{equation}
with
\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
\hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta) = \frac{1}{\pi \omega} \int_{{\cal C}_{-}} d\lambda \, \lambda S_{\lambda -1/2}(\omega) Q_{\lambda -1/2}(\cos \theta +i0)
\end{equation}
and
\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right. \right.\nonumber \\
&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right)
\end{eqnarray}
\end{subequations}
is a background integral contribution and where
\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
& & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta)
\end{eqnarray}
is a sum over the Regge poles lying in the first quadrant of the CAM plane. Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}). From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with an approximation of the differential scattering cross section (\ref{Scalar_Scattering_diff}).

@@

In this section,  we compare CAM representations or, more precisely, their Regge pole approximations with their partial wave expansions of the differential scattering cross sections.

@@

To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that have permitted us, in the Refs~\cite{Folacci:2019cmc,Folacci:2019vtt}, to reconsider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}). It is important to remark that, duo to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of these sum and integral, we have used the method described int the Appendix of Ref~\cite{Folacci:2019cmc}. It should be noted that we have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.

>>>>

\usepackage{graphicx, epsfig, amssymb}
\usepackage{amsmath, amsfonts}
\usepackage{bm}
\usepackage{enumitem}
\usepackage[usenames]{color}
\definecolor{navyblue}{rgb}{0.0, 0.0, 0.5}
\usepackage[pdftex]{hyperref}
\hypersetup
	{
		colorlinks,%
		citecolor=blue,%
		linkcolor=red,%
		urlcolor=blue,%
	}

%\usepackage[linktocpage,colorlinks=true,linkcolor=red]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{soul}
%\usepackage{enumerate}
\usepackage{pict2e}
\usepackage{diagbox}
\usepackage{empheq}

@@

\tableofcontents

\section{Introduction}

@@

In this section we describe the model for our compact object. Then we recall the partial wave expansions of the differential scattering cross section for plane monochromatic scalar waves impinging upon a compact body. Finally we apply the CAM-approach developed for black-hole scattering in \cite{Folacci:2019cmc} and \cite{Folacci:2019vtt}.

@@

  We consider that the gravitating source is a spherically symmetric incompressible perfect fluid ball of uniform
density (see Ref~\cite{Dolan:2017rtj} and references therein). In a coordinate system $\{t,r,\theta,\varphi\}$, the object is described by the metric
\begin{equation}\label{Line_elem}
  ds^2= -f(r) dt^2+h(r)^{-1}dr^2+r^2d\sigma_2^2
\end{equation}
where $d\sigma_2^2$ denotes the metric on the unit 2-sphere $S^2$. Here, the radial function $h(r)$ is continuous but not differentiable across the surface of the star $r=R$ and the function $f(r)$ is one, but not twice, differentiable. We recall that, in the exterior of the star (i.e., $r>R$), we have $f(r)=h(r)=a-2M/r$ by Birkhoff's theorem~\cite{VojeJohansen:2005nd}. In the interior of the star (i.e. $r<R$), we use the Schwarzschild solution for an incompressible fluid~\cite{Shapiro1983}

\begin{subequations}\label{Interior_Solution}
\begin{align}\label{Interior_Solution_f}
    f(r) =\frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nonumber\\ -\frac{3}{2}
                \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)},
\end{align}
\begin{equation}\label{Interior_Solution_h}
 h(r) =1-\frac{2 M r^2}{R^3}
\end{equation}
\end{subequations}

@@

We recall that, for the scalar field, the differential scattering cross section is given by (see, e.g.,\cite{Dolan:2017rtj} and references therein)
\begin{equation}\label{Scalar_Scattering_diff}
  \frac{d\sigma}{d\Omega} = |\hat{f}(\omega,\theta)|^2
\end{equation}
where
\begin{equation}\label{Scalar_Scattering_amp}
 \hat{f}(\omega,\theta) = \frac{1}{2 i \omega} \sum_{\ell = 0}^{\infty} (2\ell+1)[S_{\ell}(\omega)-1]P_{\ell}(\cos\theta)
\end{equation}
denotes the scattering amplitude.  In Eq.~(\ref{Scalar_Scattering_amp}), the functions $P_{\ell}(\cos\theta)$ are the Legendre polynomials \cite{AS65}.  We also recall that the $S$-matrix elements $S_{\ell}(\omega)$ appearing in Eq.~(\ref{Scalar_Scattering_amp}) can be defined from the modes $\phi_{\omega \ell}$ that solve the homogenous radial equation
\begin{equation}
\label{H_Radial_equation}
\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0,
\end{equation}
where $r^\ast$ denotes the tortoise coordinate defined by  $dr/dr^\ast =\sqrt{f(r)h(r)}$, and
\begin{equation}\label{Inside_Potentiel}
  V_{\ell}(r) =f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right]
\end{equation}
is the effective potential. Outside the star ($r>R$), $V_{\ell}(r)$ reduces to the Regge-Wheeler potential 
\begin{equation}\label{RW_Potentiel}
  V_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M}{r^3}\right)
\end{equation}
and the tortoise coordinates $r^\ast$ reduces to $r^\ast = r+ 2M \ln [r/(2M) -1]+\mathrm{const}$.

It is important to recall that the modes $\phi_{\omega \ell}$ should have a regular behaviour at the origin $r \to 0$
\begin{equation}\label{bc_1_in}
\phi_{\omega  \ell}(r) \scriptstyle{\underset{r \to 0}{\sim}}.
\displaystyle{r^{\ell+1}}.
\end{equation}
The asymptotic behaviour of the modes at spatial infinity $r \to +\infty$ (i.e., for $r_\ast \to +\infty$) is 
\begin{equation}\label{bc_2_in}
\phi_{\omega  \ell}(r) \scriptstyle{\underset{r_\ast \to +\infty}{\sim}}
\displaystyle{ A^{(-)}_\ell (\omega) e^{-i\omega r_\ast} + A^{(+)}_\ell (\omega) e^{+i\omega r_\ast}}.
\end{equation}
In this last equation, the coefficients $A^{(-)}_\ell (\omega)$ and  $A^{(+)}_\ell (\omega)$ are complex amplitudes and we have
\begin{equation}\label{Matrix_S}
  S_{\ell}(\omega) =  e^{i(\ell+1)\pi} \, \frac{A_{\ell}^{(+)}(\omega)}{A_{\ell}^{(-)}(\omega)}.
\end{equation}

@@

By using the Sommerfeld-Watson transformation \cite{Watson18,Sommerfeld49,Newton:1982qc} which permits us to write
\begin{equation}\label{SWT_gen}
\sum_{\ell=0}^{+\infty} (-1)^\ell F(\ell)= \frac{i}{2} \int_{\cal C} d\lambda \, \frac{F(\lambda -1/2)}{\cos (\pi \lambda)}
\end{equation}
with a function $F$ without any singularities on the real $\lambda$ axis, we replace the discrete sum over the ordinary angular momentum $\ell$ in Eq.~(\ref{Scalar_Scattering_amp}) by a contour integral in the complex $\lambda$ plane (i.e., in the complex $\ell$ plane with $\lambda = \ell +1/2$). By noting that $P_\ell (\cos \theta)=(-1)^\ell P_\ell (-\cos \theta)$, we obtain
\begin{eqnarray}\label{SW_Scalar_Scattering_amp}
& & \hat{f}(\omega,\theta) = \frac{1}{2 \omega}  \int_{\cal C} d\lambda \, \frac{\lambda}{\cos (\pi \lambda)} \nonumber \\
&&  \qquad\qquad   \times \left[ S_{\lambda -1/2} (\omega) -1 \right]P_{\lambda -1/2} (-\cos \theta).
\end{eqnarray}
In Eqs.~(\ref{SWT_gen}) and (\ref{SW_Scalar_Scattering_amp}), the integration contour encircles counterclockwise the positive real axis of the complex $\lambda$ plane, i.e., we take ${\cal C}=]+\infty +i\epsilon,+i\epsilon] \cup
[+i\epsilon,-i\epsilon] \cup [-i\epsilon, +\infty -i\epsilon[$ with $\epsilon \to 0_+$ (see Fig.1 Ref~\cite{Folacci:2019cmc}).

The Legendre function of first kind $P_{\lambda -1/2} (z)$ denotes the analytic extension of the Legendre polynomials $P_\ell (z)$. It is defined in terms of hypergeometric functions by \cite{AS65}
\begin{equation}\label{Def_ext_LegendreP}
P_{\lambda -1/2} (z) = F[1/2-\lambda,1/2+\lambda;1;(1-z)/2].
\end{equation}
In Eq.~(\ref{SW_Scalar_Scattering_amp}), $S_{\lambda -1/2} (\omega)$ denotes ``the'' analytic extension of $S_\ell (\omega)$. It is given by [see Eq.~(\ref{Matrix_S})]
\begin{equation}\label{Matrix_S_CAM}
  S_{\lambda -1/2}(\omega) =  e^{i(\lambda + 1/2)\pi} \, \frac{A_{\lambda -1/2}^{(+)}(\omega)}{A_{\lambda -1/2}^{(-)}(\omega)}
\end{equation}
where the complex amplitudes $A^{(-)}_{\lambda -1/2} (\omega)$ and  $A^{(+)}_{\lambda -1/2} (\omega)$ are defined from the analytic extension of the modes $\phi_{\omega \ell}$, i.e., from the function $\phi_{\omega ,\lambda -1/2}$.

It is important to note that the poles of  $S_{\lambda -1/2} (\omega)$ in the complex $\lambda$ plan (i.e., the Regge poles) are defined  as  the zeros $\lambda_n(\omega)$ with $n=1,2,3,\ldots$ of the coefficient  $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{PR_def_Am}
A^{(-)}_{\lambda_n(\omega)-1/2} (\omega)=0.
\end{equation}
The residue of the matrix $S_{\lambda-1/2}(\omega)$ at the pole $\lambda=\lambda_n(\omega)$ is defined by [see Eq.~(\ref{Matrix_S_CAM})]
\begin{equation}\label{residues_RP}
r_n(\omega)=e^{i\pi [\lambda_n(\omega)+1/2]} \left[ \frac{A_{\lambda -1/2}^{(+)}(\omega)}{\frac{d}{d \lambda}A_{\lambda -1/2}^{(-)}(\omega)}\right]_{\lambda=\lambda_n(\omega)}.
\end{equation}
These residues play a central role in the complex angular momentum paradigm.

Now, we ``deform'' the contour ${\cal C}$ in Eq.~(\ref{SW_Scalar_Scattering_amp}) in order to collect, by using Cauchy's theorem, the Regge poles contributions. This is achieved by following, \textit{mutatis mutandis}, the approach developed in Ref~\cite{Folacci:2019cmc} (see more particularly Sec. IIB~3 and Fig.~1). We obtain

\begin{equation}\label{CAM_Scalar_Scattering_amp_tot}
\hat{f} (\omega, \theta) =  \hat{f}^\text{\tiny{B}} (\omega, \theta) +  \hat{f}^\text{\tiny{RP}} (\omega, \theta)
\end{equation}
where
\begin{subequations}\label{CAM_Scalar_Scattering_amp_decomp}
\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background}
\hat{f}^\text{\tiny{B}} (\omega, \theta) = \hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta)+ \hat{f}^\text{\tiny{B},\tiny{Im}} (\omega, \theta)
\end{equation}
is a background integral contribution with
\begin{equation}\label{CAM_Scalar_Scattering_amp_decomp_Background_a}
\hat{f}^\text{\tiny{B},\tiny{Re}} (\omega, \theta) = \frac{1}{\pi \omega} \int_{{\cal C}_{-}} d\lambda \, \lambda S_{\lambda -1/2}(\omega) Q_{\lambda -1/2}(\cos \theta +i0)
\end{equation}
and
\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_Background_b}
\hat{f}^\text{\tiny{B},\tiny{Im}} && (\omega, \theta) = \frac{1}{2 \omega}\left(\int_{+i\infty}^{0} d\lambda \, \left[S_{\lambda -1/2}(\omega) P_{\lambda_n(\omega) -1/2} (-\cos \theta) \right. \right.\nonumber \\
&& -\left. \left. S_{-\lambda -1/2}(\omega) e^{i \pi \left(\lambda+1/2\right)}P_{\lambda_n(\omega) -1/2} (\cos \theta) \right]\lambda\right)
\end{eqnarray}
\end{subequations}
The second term in Eq.~(\ref{CAM_Scalar_Scattering_amp_tot}) ,
\begin{eqnarray}\label{CAM_Scalar_Scattering_amp_decomp_RP}
& & \hat{f}^\text{\tiny{RP}} (\omega, \theta) = -\frac{i \pi}{\omega}    \sum_{n=1}^{+\infty}   \frac{ \lambda_n(\omega) r_n(\omega)}{\cos[\pi \lambda_n(\omega)]}  \nonumber \\
&&  \qquad\qquad \qquad\qquad \times  P_{\lambda_n(\omega) -1/2} (-\cos \theta),
\end{eqnarray}
is a sum over the Regge poles lying in the first quadrant of the CAM plane. Of course, Eqs.~(\ref{CAM_Scalar_Scattering_amp_tot}), (\ref{CAM_Scalar_Scattering_amp_decomp}) and (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) provide an exact representation of the scattering amplitude $\hat{f} (\omega, \theta)$ for the scalar field, equivalent to the initial partial wave expansion (\ref{Scalar_Scattering_amp}). From this CAM representation, we can extract the contribution $\hat{f}^\text{\tiny{RP}} (\omega, \theta)$ given by (\ref{CAM_Scalar_Scattering_amp_decomp_RP}) which, as a sum over Regge poles, is only an approximation of $\hat{f} (\omega, \theta)$, and which provides us with an approximation of the differential scattering cross section (\ref{Scalar_Scattering_diff}).

@@

In this section,  we compare the partial wave expansions of the differential scattering cross sections with their equivalent CAM representations or, more precisely, their Regge pole approximations.

@@

To construct the scattering amplitude \eqref{Scalar_Scattering_amp}, the back ground integrals~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} and~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_b} as well as the Regge pole contribution~\eqref{CAM_Scalar_Scattering_amp_decomp_RP}, we use, \textit{mutatis mutandis} the computational methods that permitted one of us, in Refs~\cite{Folacci:2019cmc,Folacci:2019vtt} to consider the CAM representation for scattering of the scalar, electromagnetic and gravitational waves by Schwarzschild BH (see also Ref~\cite{Dolan:2017rtj}). It is important to remark that, duo to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} suffer a lack of convergence and to overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}. We have performed all the numerical calculations by using {\it Mathematica} \cite{Mathematica}.
